### 2012-10-29 Dissertation/lists.tex
Full refactoring of main file

\listoffigures
\addcontentsline{toc}{chapter}{Список иллюстраций}
\clearpage

\listoftables
\addcontentsline{toc}{chapter}{Список таблиц}
\clearpage