### 2012-10-29 Dissertation/lists.tex
Small fix of preamble

\listoffigures
\addcontentsline{toc}{chapter}{\listfigurename}
\clearpage

\listoftables
\addcontentsline{toc}{chapter}{\listtablename}
\clearpage