### 2012-11-01 Dissertation/referenses.tex
Add work with BibTeX

\addcontentsline{toc}{chapter}{\bibname}
\bibliography{biblio}