### 2012-11-08 Dissertation/dissertation.tex
Add more pretty comments

\documentclass[a4paper,12pt]{report}

\input{packages}		% Подключаемые пакеты
\input{styles}			% Пользовательские стили

\begin{document}

\input{names}			% Переопределение именований

\input{title}			% Титульный лист
\input{contents}		% Оглавление
\input{introduction}	% Введение
\input{part1}			% Глава 1
\input{part2}			% Глава 2
\input{part3}			% Глава 3
\input{conclusion}		% Заключение
\input{lists}			% Списки таблиц и изображений
\input{referenses}		% Список литературы
\input{appendix}		% Приложения

\end{document}