### 2012-11-08 Dissertation/lists.tex

\listoffigures									% Список изображений
\addcontentsline{toc}{chapter}{\listfigurename}	% Добавляем на него ссылку в оглавление
\clearpage

\listoftables									% Список таблиц
\addcontentsline{toc}{chapter}{\listtablename}	% Добавляем на него ссылку в оглавление
\clearpage