### 2015-01-11 Dissertation/lists.tex

\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{\listfigurename}
\listoffigures									% Список изображений
\newpage

\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{\listtablename}
\listoftables									% Список таблиц
\newpage