### 2015-01-11 Dissertation/title.tex
Add data.tex in disseration template

\thispagestyle{empty}

\begin{center}
\thesisOrganization \par
\par
\end{center}

\vspace{20mm}
\begin{flushright}
На правах рукописи

{\sl УДК \thesisUdk}
\end{flushright}

\vspace{30mm}
\begin{center}
{\large \thesisAuthor}
\end{center}

\vspace{5mm}
\begin{center}
{\bf \large \thesisTitle
\par}

\vspace{10mm}
{%\small
Специальность \thesisSpecialtyNumber~---

<<\thesisSpecialtyTitle>>
}

\vspace{10mm}
Диссертация на соискание учёной степени

\thesisDegree
\end{center}

\vspace{20mm}
\begin{flushright}
Научный руководитель:

\supervisorRegalia

\supervisorFio

\end{flushright}

\vspace{20mm}
\begin{center}
{\thesisCity~--- \thesisYear}
\end{center}

\newpage