### 2016-07-05 Dissertation/lists.tex

\clearpage
\listoffigures									% Список изображений

%%% Список таблиц %%%
% (ГОСТ Р 7.0.11-2011, 5.3.10)
\clearpage
\listoftables									% Список таблиц
\newpage