### 2016-07-27 Dissertation/lists.tex

\clearpage
\ifthenelse{\NOT \isundefined{\microtypesetup}}{\microtypesetup{protrusion=false}}{} % не рекомендуется применять пакет микротипографики к автоматически генерируемым спискам
\listoffigures  % Список изображений

%%% Список таблиц %%%
% (ГОСТ Р 7.0.11-2011, 5.3.10)
\clearpage
\listoftables   % Список таблиц
\ifthenelse{\NOT \isundefined{\microtypesetup}}{\microtypesetup{protrusion=true}}{}
\newpage