### 2019-03-08 presentation.tex

\documentclass[14pt, xcolor={dvipsnames, table, hyperref, cmyk}, utf8]{beamer}

\input{common/setup}          % общие настройки шаблона
\input{common/packages}       % Пакеты общие для диссертации и автореферата
\input{common/data}           % Основные сведения
\input{common/fonts}          % Определение шрифтов (частичное)

\input{Presentation/prespreamble.tex}	% Настройки

\begin{document}
\maketitle
\input{Presentation/prescontent.tex}
\end{document}