### 2021-02-05 Dissertation/acronyms.tex

\printnomenclature[3.5cm] % Значение ширины столбца с обозначениями стоит подбирать вручную