### 2024-02-08 Dissertation/appendix.tex
dissertation_v2: Dissertation/appendix.tex

\chapter*{Приложение А.\\Компьютерное моделирование конечномерных квантовых систем}\label{app:A}
\addcontentsline{toc}{chapter}{Приложение А. Компьютерное моделирование конечномерных\newline\indent\hspace{50pt}квантовых систем}
%---------------------------------------------------------------------------------------------------------------------------------